A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-02-17 paper/discussion.tex
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures

>>>>

\begin{figure}
\epsscale{1.00}
\plotone{fig/scattering_plots.png}
\caption{Covariance of parameters for one small box}
\label{graph_scattering_plots}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
\label{graph_SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. }
\label{graph_SFR_DMHM_w}
\end{figure}

### 2015-02-17 paper/observations.tex
Willott observations paragraph added, also SFR vs. DM (w/wo dust)figures

This paper is based on three main observation sets. The most recent is from the
Hubble Space Telescope, this observations where performed by \cite{bouwens14}.
The second set is from the Canada-France Hawaii Telescope, \cite{willott13} and
the last one by the UK Infrared Telescope and the Subaru Telescope
\cite{mclure09}. Those observations where made using the Frop-out technique.

The data from the HST is a compilation of previous works since
2006 \citep{bouwens06}, wich includes also observations after the 2009
upgrade mission\citep{bouwens12}.

@@

>>>>

This paper is based on four main observational data sets. The most recent is
from the Hubble Space Telescope Legacy plus ground telescopes \citep{bouwens14}.
The second set is from the Canada-France Hawaii Telescope\citep{willott13} and
the last one by the UK Infrared Telescope and the Subaru Telescope
\cite{mclure09}. Those observations where made using the Drop-out technique.

The data from the HSTL is a compilation of previous works since
2006 \citep{bouwens06}, wich includes also observations after the 2009
upgrade mission\citep{bouwens12}. They estimate the uncertainty in their LF due
to cosmic variance. Taking account they used five independent surveys, they get
jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
developed by Trenti \& Stiavelli (2008).

@@

Willott et al. \cite{willott13} presented the sixth release of the Canada-France-Hawaii Telescope Legacy Survey CFHTLS. The observations where performed over four separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this survey great robustness.
Optical observations used MegaCam with $u^* g' r' i' z'$ filters. The main selection criteria: all the objects must be brighter than magnitude $z' = 25.3$. The final number of LBGs founded was 40. Moreover, they get spectroscopic confirmation for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which has a field of view $\ll 1 \deg^2$. They show incompleteness in the sample due to foreground contamination and the detection algorithm; there is no warranty to have every object brighter than the limit magnitude on the faint limit. The full galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey was focussed on the highly luminous LBGs. LF is calculated using the stepwise maximum likelihood method of Efstathiu et al. [Cite required!!!], within magnitudes from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows an exponential decline at the bright end, where feedback processes and inefficient last cooling limites star forming in bright galaxies hosted in the most massive halos.
